\protect Quantitative patterns in drone wars

### 2025-01-27 correspondence/2022-05-31response-epj-data-science.body.tex
Solid update; moving to manuscipt format

Again for baby girl names in Fig. 4, here's the extracted display of balances:
\begin{center}
  \includegraphics[width=0.3\textwidth]{figallotax-baby-girl-name-balances.pdf}
\end{center}

@@

\begin{center}
  \includegraphics[width=0.4\columnwidth]{allotaxonograph_balances2_flattened-crop.pdf}
\end{center}
\begin{excerpt}
  \textbf{Fig.~1G}:
  For all allotaxonographs, we show balances at the bottom right
  of the rank-rank histogram.
  Two kinds of exclusive type comparisons for the numbers of types in each system
  are recorded in the bottom two bars,
  while the top bar conveys information about type sizes.
  The top bar is rendered only when sizes are known
  (this is the only part of the allotaxonographs that is not
  determined purely from type rankings).
  In the present paper, we work from datasets with known type sizes,
  and all allotaxonographs will have all three bars.
  All balances show normalized quantities rather than absolute numbers

@@

\includegraphics[width=\textwidth]{figallotaxonometer9000-siblis_alphasweep_05-2007-Q4_2018-Q4_marketcaps004_noname.pdf}

\includegraphics[width=\textwidth]{figallotaxonometer9000-siblis_alphasweep_06-2007-Q4_2018-Q4_marketcaps004_corrected_noname.pdf}

@@

\includegraphics[width=\textwidth]{figtruncation.pdf}

@@

\includegraphics[width=\textwidth]{figallotaxonometer9000-babynames-rtd-010-alpha-infty-1-140-1880-vs-2020_noname.pdf}

@@

\includegraphics[width=\textwidth]{figallotaxonometer9000-babynames-rtd-010-alpha-infty-2-140-1880-vs-2020_noname.pdf}

>>>>

Again for baby girl names in Fig. 4, here's the extracted display of balances:
\begin{center}
  \includegraphics[width=0.3\textwidth]{figures/localized/figallotax-baby-girl-name-balances.pdf}
\end{center}

@@

\begin{center}
  \includegraphics[width=0.4\columnwidth]{figures/localized/allotaxonograph_balances2_flattened-crop.pdf}
\end{center}
\begin{excerpt}
  \textbf{Fig.~1G}:
  For all allotaxonographs, we show balances at the bottom right
  of the rank-rank histogram.
  Two kinds of exclusive type comparisons for the numbers of types in each system
  are recorded in the bottom two bars,
  while the top bar conveys information about type sizes.
  The top bar is rendered only when sizes are known
  (this is the only part of the allotaxonographs that is not
  determined purely from type rankings).
  In the present paper, we work from datasets with known type sizes,
  and all allotaxonographs will have all three bars.
  All balances show normalized quantities rather than absolute numbers

@@

\includegraphics[width=\textwidth]{figures/localized/figallotaxonometer9000-siblis_alphasweep_05-2007-Q4_2018-Q4_marketcaps004_noname.pdf}

\includegraphics[width=\textwidth]{figures/localized/figallotaxonometer9000-siblis_alphasweep_06-2007-Q4_2018-Q4_marketcaps004_corrected_noname.pdf}

@@

\includegraphics[width=\textwidth]{figures/localized/figtruncation.pdf}

@@

\includegraphics[width=\textwidth]{figures/localized/figallotaxonometer9000-babynames-rtd-010-alpha-infty-1-140-1880-vs-2020_noname.pdf}

@@

\includegraphics[width=\textwidth]{figures/localized/figallotaxonometer9000-babynames-rtd-010-alpha-infty-2-140-1880-vs-2020_noname.pdf}
